Local metal-insulator transition in a generalised Anderson impurity model

### 2022-05-05 gen-siam-manuscript/gen-siam.tex
--no-message

Quantum impurity models, owing to their simple construction, have often served as testbeds for analytical and numerical methods, as well as experimental techniques. They consist of one or more local correlated quantum system(s) coupled with (typically non-interacting) bosonic or fermionic conduction bath channel(s). Even though the impurity itself is simple, the interaction with the bath often leads to novel phases, and such impurity systems often lead to interesting phenomena that have far-reaching consequences and require fundamental theoretical breakthroughs in order to understand them. One of the most well-studied impurity models is the single-impurity Anderson model; it consists of a single impurity site of spin-half electrons and local correlation \(U\) hybridising with a non-interacting conduction bath through a coupling \(V\).

>>>>

Quantum impurity models, owing to their simple construction, have often served as testbeds for analytical and numerical methods, as well as experimental techniques. They consist of one or more local correlated quantum system(s) coupled with (typically non-interacting) bosonic or fermionic conduction bath channel(s). Even though the impurity itself is simple, the interaction with the bath often leads to novel phases, and such impurity systems often lead to interesting phenomena that have far-reaching consequences and require fundamental theoretical breakthroughs in order to understand them. One of the most well-studied impurity models is the single-impurity Anderson model; it consists of a single impurity site of spin-half electrons and local correlation \(U\) hybridising with a non-interacting conduction bath through a coupling \(V\). One of the most well-studied of these is the single-impurity Anderson model~\cite{anderson_1961,anderson_1978} (AIM), consisting of a single correlated impurity site coupled with a non-interacting conduction bath. The model combines localisation arising from Mott physics~\cite{Mott_1949,vanvleck_1953} and delocalisation of the impurity arising from virtual resonance with the conduction bath~\cite{friedel_1956}.
